Model

### 2020-02-10 stats/model.Rmd
update model file for comparison

model_pred <- readRDS("../saves/model_pred.rds")

@@

global_params <- readRDS("../saves/global_params.rds")

@@

subject_sigma <- readRDS("../saves/subject_sigma_re.rds")

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(run ~parameter + item, scales = 'free')+
  theme_few()

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(run~type + parameter, scales = 'free')+
  theme_few()

@@

```{r}
plot_item_sigma <- ggplot(item_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(run ~type + parameter, scales = 'free')+
  theme_few()

@@

```{r}
plotg_subj_sigma <- ggplot(subject_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Subject Sigma")+
  theme_few()

@@

# cor_prag_chain <- model_pred_prag%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(chain, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))

@@

# cor_prior <- model_pred_prior%>%
#   mutate(age = as.numeric(age) + min(data_comb$age_num),
#          age = cut(age, 
#                       breaks = c(2,3,4,5),
#                       labels = c(2,3,4)))%>%
#   group_by(model, alignment, item, age)%>%
#   summarise(model_mean = estimate_mode(pred),
#             model_ci_lower = hdi_lower(pred),
#             model_ci_upper = hdi_upper(pred))

cor_model_pred <- bind_rows(
  #cor_prag_chain,
  cor_prag,
  cor_global,
  cor_flat,
  cor_prior
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      # binnned_data%>%mutate(model = "pragmatic", chain = 1),
      # binnned_data%>%mutate(model = "pragmatic", chain = 2),
      # binnned_data%>%mutate(model = "pragmatic", chain = 3),
      # binnned_data%>%mutate(model = "pragmatic", chain = 4),
      # binnned_data%>%mutate(model = "pragmatic", chain = 5),
      # binnned_data%>%mutate(model = "pragmatic", chain = 6)
      binnned_data%>%mutate(model = "pragmatic"),
      binnned_data%>%mutate(model = "global"),
      binnned_data%>%mutate(model = "flat"),
      binnned_data%>%mutate(model = "prior")
      )
  )

@@

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(model~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")+
  guides(col = F)
```

@@

log_like_prag <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month)%>%
  left_join(plot_model_pred_prag)%>%
  mutate(like = ifelse(correct == 1, mean, 1 - mean),
         log_like_prag = log(like))%>%
  select(age, alignment,item,log_like_prag)

log_like_global <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month)%>%
  left_join(plot_model_pred_global)%>%
  mutate(like = ifelse(correct == 1, mean, 1 - mean),
         log_like_global = log(like))%>%
  select(age, alignment,item,log_like_global)

log_like_flat <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month)%>%
  left_join(plot_model_pred_flat)%>%
  mutate(like = ifelse(correct == 1, mean, 1 - mean),
         log_like_flat = log(like))%>%
  select(age, alignment,item,log_like_flat)

>>>>

@@

global_params <- readRDS("../saves/global_params.rds")%>%
  filter(chain != 6)

@@

#subject_sigma <- readRDS("../saves/subject_sigma.rds")

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

@@

```{r}
plot_item_sigma <- ggplot(item_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()

@@

```{r}
plotg_subj_sigma <- ggplot(subject_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Subject Sigma")+
  facet_grid(~parameter)+
  theme_few()

@@

cor_prag_chain <- model_pred_prag%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age,
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(chain, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

@@

cor_prior <- model_pred_prior%>%
  mutate(age = as.numeric(age) + min(data_comb$age_num),
         age = cut(age,
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

cor_model_pred <- bind_rows(
  cor_prag_chain,
  # cor_prag,
  # cor_global,
  # cor_flat,
  # cor_prior
)

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      binnned_data%>%mutate(model = "pragmatic", chain = 1),
      binnned_data%>%mutate(model = "pragmatic", chain = 2),
      binnned_data%>%mutate(model = "pragmatic", chain = 3),
      binnned_data%>%mutate(model = "pragmatic", chain = 4),
      binnned_data%>%mutate(model = "pragmatic", chain = 5),
      binnned_data%>%mutate(model = "pragmatic", chain = 6)
      # binnned_data%>%mutate(model = "pragmatic"),
      # binnned_data%>%mutate(model = "global"),
      # binnned_data%>%mutate(model = "flat"),
      # binnned_data%>%mutate(model = "prior")
      )
  )

@@

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(chain~age)+
  theme_few() + 
  scale_colour_ptol(name ="Alignment")+
  guides(col = F)
```

@@

data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(model_pred_prag)%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_prag = log(like))%>%
  select(chain, iteration, age, alignment,item,log_like_prag)%>%
  saveRDS(.,"../saves/log_like_prag")

log_like_global <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(model_pred_global)%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_global = log(like))%>%
  select(chain,iteration, age, alignment,item,log_like_global)

log_like_flat <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(model_pred_flat)%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_flat = log(like))%>%
  select(chain,iteration,age, alignment,item,log_like_flat)
